Performance of two different ontological and data access methods

### 2014-07-08 cold2014/magnus.tex
some low-hanging fruit for shortening
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@739 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subtitle{---Draft submitted to COLD 2014---}

@@

The retrieval of information from different sources and then combine
them to allow a user to find a certain combination of properties that
suit their purpose is an archetypal Semantic Web use case. We have
chosen to focus on a product selection use case, specifically on cars,
since some car manufacturers have embraced the Semantic Web vision and chosen
to share detailed data on their products.

@@

A central difference with these ontologies is that CO allows the
configuration to be defined in terms of classes, whereas VSO
represents them with properties, for example:
\begin{lstlisting}[basicstyle=\tiny, frame=single]
#CO representation of fuel type
:var_PT1628  a           co:ConfigurationVariable , owl:Class ;
        rdfs:label       "Fuel Type"@en ;
        co:confVarId   "PT1628" ;
        co:hasValue    
	    <http://uk.co.rplug.renault.com/product/gen/spec/PT1628_diesel/-#this> .

@@

The Volkswagen solution builds upon GoodRelations\cite{GRQual}, which
is a web vocabulary for e-commerce and was launched in 2008 and is now
widespread.  GoodRelations can be used for detailed information about
products to be sold online.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself an important contribution, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using semantic technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{python} script into the
ontologies developed by Martin Hepp and Volkswagen.

To be able to put large stress on the application, which again would
allow us to bring out key strengths and weaknesses of the two
different approaches, we chose to create an application where a user
choose several or all car options specifications.

The application was implemented using Apache Maven, Spring and Apache
Tomcat as well as Jena.

@@

\subsection{Full factorial experiment}
A full factorial experiment is when one got $k$ factors and $n$ amount
of levels. This means that there is $n^k$ \emph{factorial designs}
which result in $n^k$ designs to execute.  We have chosen only
two-level experiments for this research, but the factors may vary. This
means that we will use a $2^k$ full factorial design for every
experiment. The experiments consist of $2^k$ combinations with $k$
factors. For instance if we have three factors where every factor got
two levels we get $2^3$ designs, also called \emph{runs}. This results
in a \emph{planning matrix} that shows the actual runs in the
experiment.

>>>>

%\subtitle{---Draft submitted to COLD 2014---}

@@

The retrieval of information from different sources and then combine
them to allow a user to find a certain combination of properties that
suit their purpose is an archetypal Semantic Web use case. We have
chosen to focus on a product selection use case, specifically on cars,
since some car-makers have embraced the Semantic Web vision and chosen
to share detailed data on their products.

@@

A key difference with these ontologies is that CO allows the
configuration to be defined in terms of classes, while VSO
represents them with properties, e.g:
\begin{lstlisting}[basicstyle=\tiny, frame=single]
#CO representation of fuel type
:var_PT1628  a           co:ConfigurationVariable , owl:Class ;
        rdfs:label       "Fuel Type"@en ;
        co:confVarId   "PT1628" ;
        co:hasValue    
	    <http://uk.co.rplug.renault.com/product/gen/spec/PT1628_diesel/-#this> .

@@

Volkswagen builds upon GoodRelations\cite{GRQual}, which
is a web vocabulary for e-commerce that was launched in 2008 and is now
widespread.  GoodRelations can be used for detailed information about
products to be sold online.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself an important contribution, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using semantic technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{Python} script into the
ontologies developed by Martin Hepp and Volkswagen.

To be able to put large stress on the application, which again would
allow us to bring out key strengths and weaknesses of the two
different approaches, we chose to create an application where a user
choose several or all car options specifications. The application was
implemented using Apache Maven, Spring and Apache Tomcat as well as
Jena.

@@

\subsection{Full factorial experiment}
A full factorial experiment is when one got $k$ factors and $n$ amount
of levels. This means that there is $n^k$ \emph{factorial designs}
which result in $n^k$ designs to execute.  We have chosen only
two-level experiments for this research, but the factors may
vary. This means that we will use a $2^k$ full factorial design for
every experiment. The experiments consist of $2^k$ combinations with
$k$ factors. This results in a \emph{planning matrix} that shows the
actual runs in the experiment.
